The Name of the Title is Hope

### 2020-03-19 abstract.tex
abstract and methods update

\begin{abstract}
    Abstracts are scary.
\end{abstract}

>>>>

\begin{abstract}
Program synthesis has been focusing on making newer and better tools; however,
few have evaluated how people like to interact with them and what features users
find useful.
%
We evaluate the addition of examples to type directed program synthesis.
%
We measured 10 participants between two variants, each with 4 tasks.
%
We do not find a statistical significance, in general, with the addition of
examples.
%
We do note, that one task did have a significant difference in performance
between groups.
%
Further evaluation is needed to determine a reason for this.
\end{abstract}

### 2020-03-19 methods.tex
consistency is key
abstract and methods update

% Ecological Validity:
% Why does your study answer your research question? Why
% does your evaluation address your hypothesis? Make sure your study, and the
% variables you're measuring, properly address the question you are asking.
\subsection{Measures}
For each participant, we measured:
\begin{itemize}
    \item Time-to-correct solution (per task)
    \item Count of incorrect guesses (per task)
    \item Count and type of interpreter queries (across all tasks)
\end{itemize}

>>>>

% Ecological Validity:
% Why does your study answer your research question? Why
% does your evaluation address your hypothesis? Make sure your study, and the
% variables you're measuring, properly address the question you are asking.
\subsection{Measures}
We gathered 10 participants from around our department's building and from the
local Hillcrest community.
%
We required that participants be able to read some Haskell code.

For each participant, we measured:
\begin{itemize}
    \item Time-to-correct solution (per task)
    \item Count of incorrect selections (per task)
    \item Count and type of interpreter queries (across all tasks)
\end{itemize}
